Supplements for the manuscript `TANGO: A reliable, open-source, browser-based task to assess individual differences in gaze understanding in 3 to 5-year-old children and adults'

### 2023-05-12 stats/supplements_validity.Rmd
incorporate reviews round 2

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(ggpubr)
library(ggthemes)
library(brms) # modeling
library(tidyverse) # data handling etc.
library(tidybayes) # gather_draws

@@

```{r orev_plot}
orev_plot <- ggplot(mDataOrev, aes(x = mean_orev, y = mean_tango)) +

  geom_point(aes(col = as.factor(ageInYears)), shape = 18, size = 2) +
  geom_smooth(method = "glm", size = 0.5, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0.9, label.y = 0.975, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +

  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D"), labels = c("3-year-olds", "4-year-olds", "5-year-olds", "6-year-olds", "7-year-olds")) +

  labs(x = "oREV score", y = "TANGO score", col = "Age in years") + 
  scale_x_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.25)) +

  theme(legend.title = element_text(size = 9), 
        legend.text = element_text(size = 9),
        legend.key.size = unit(0.4, "cm"), 
        legend.direction = "vertical", 
        legend.box = "horizontal",
        legend.position = c(0.175, 0.25), 
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black")
        )

@@

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(ggpubr)
library(ggthemes)
library(brms) # modeling
library(tidyverse) # data handling etc.
library(tidybayes) # gather_draws
library(ggtext) # for printing italics

@@

```{r orev_plot}
orev_data %>%
  group_by(ageInYears) %>%
  summarize(cor=cor(mean_tango, mean_orev) %>% round(2))

orev_plot <- ggplot(orev_data, aes( x = mean_tango, y = mean_orev)) +

  geom_jitter(aes(col = as.factor(ageInYears)), shape = 18, size = 2, width = 0.05, height = 0.05) +
  geom_smooth(method = "glm", size = 1, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0.9, label.y = 0.98, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +

  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D"), labels = c("3-year-olds (*r* = 0.26)", "4-year-olds (*r* = 0.22)", "5-year-olds (*r* = 0.29)", "6-year-olds (*r* = 0.11)", "7-year-olds (*r* = 0.40)")) +

  labs(x = "TANGO score", y = "oREV score", col = "Age in years") + 
  scale_x_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.25)) + 
  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1, 0.25)) +

  theme(legend.title = element_text(size = 9), 
        legend.key.size = unit(0.4, "cm"), 
        legend.direction = "vertical", 
        legend.box = "horizontal",
        legend.position = c(0.2, 0.18), 
        legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"), 
        legend.text = element_markdown()
        )

@@

```{r orev_by_agegroup}
orev_agegroup <- ggplot(orev_data, aes( x = mean_tango, y = mean_orev)) +

  geom_jitter(aes(col = as.factor(ageInYears)), shape = 18, size = 2, width = 0.05, height = 0.05) +
  geom_smooth(method = "glm", size = 1, alpha = 0.15, col = "darkgrey") +
  stat_cor(method = "pearson", label.x = 0.05, label.y = 1.1, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +

  scale_color_manual(values = c("#c6d325", "#00b1ea", "#29485d", "#9D3BBD", "#F71C8D"), labels = c("3-year-olds (*r* = 0.26)", "4-year-olds (*r* = 0.22)", "5-year-olds (*r* = 0.29)", "6-year-olds (*r* = 0.11)", "7-year-olds (*r* = 0.40)")) +

  labs(x = "TANGO score", y = "oREV score", col = "Age in years") + 
  scale_x_continuous(limits = c(0, 1.05), breaks = seq(0, 1, 0.5)) + 
  scale_y_continuous(limits = c(0, 1.1), breaks = seq(0, 1, 0.25)) +
  facet_grid(~ ageInYears) + 
  theme(legend.position = "none")
d
orev_agegroup

saveRDS(orev_agegroup, file = "../saves/tango_orev_byagegroup.rds")
ggsave("../figures/tango_supplements_orev_byagegroup.png", width = 7, height = 4)
```

### 2023-05-12 supplements/supplements.Rmd
incorporate reviews round 2

```{r reli_agegroup, include=FALSE}
hedge_intCon_agegroup <- readRDS("../saves/tango-hedge-intCon-kids.rds") + 
  geom_point(aes(col = ageInYears), size = 1) + 
  facet_wrap(~ ageInYears)

hedge_retest_agegroup <- readRDS("../saves/tango-hedge-retest-kids.rds") + 
  geom_point(aes(col = ageInYears), size = 1) + 
  facet_wrap(~ ageInYears)

box_intCon_agegroup <- readRDS("../saves/tango-box-intCon-kids.rds") + 
  geom_point(aes(col = ageInYears), size = 1) + 
  facet_wrap(~ ageInYears)

box_retest_agegroup <- readRDS("../saves/tango-box-retest-kids.rds") + 
  geom_point(aes(col = ageInYears), size = 1) + 
  facet_wrap(~ ageInYears)

ggarrange(hedge_intCon_agegroup, 
          hedge_retest_agegroup,
          box_intCon_agegroup, 
          box_retest_agegroup, 
          ncol = 2,
          nrow = 2, 
          labels = c("A", "B", "C", "D")
)

ggsave("../figures/tango_supplements_reli_byagegroup.png", width = 9, height = 6)
```

@@

### Analysis
To estimate the effect of gaze understanding on receptive vocabulary, we fitted a GLMM predicting the task performance by the gaze understanding score (scaled), controlling for age: `cor_clt | trials(n_clt) ~ age_centered + mean_gaze_centered`). We modelled the number of participant's correct responses using a `Binomial` distribution.

@@

>>>>

@@

### Analysis
To estimate the effect of gaze understanding on receptive vocabulary, we fitted a GLMM predicting the task performance by the gaze understanding score (scaled), controlling for age: `cor_clt | trials(n_clt) ~ age_centered + mean_gaze_centered`). We modelled the number of participant's correct responses using a `Binomial` distribution.
In order to combine data of our two TANGO study versions, we transformed continuous click responses from the hedge version into a discrete outcome. After this transformation, we calculated a "TANGO score" as the proportion of correctly located targets. See Analysis section of Social-environmental factors for further detail.

@@

(ref:figlab6) **Effect of gaze understanding on receptive vocabulary by age group**. Regression lines with 95% CI show smooth conditional mean based on a linear model (generalized linear model for box version), with *Pearson*'s correlation coefficient *r*. Diamonds show the performance for each subject. The color of data points denotes age group.

```{r fig6, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab6)"}
knitr::include_graphics("../figures/tango_supplements_orev_byagegroup.png")
```
